---
title: "Getting started - MTXQCvX2"
author:
- affiliation: Kempa Lab, BIMSB/MDC-Berlin 
  name: Christin Zasada
date: "27 October 2017"
output: html_document
params:
  spath:
    input: text
    label: "Create MTXQCproject subfolder:"
    value: ""
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


### Welcome to the MTXQC universe.

This document provides you a quick guidance through the first steps of the MTXQC universe and how to setup your R-studio project. 

Detailed information to distinct steps are provided in addition in the MTXQC-OneNotebook [^1]. You need to setup a microsoft office account or need to remember your credentials. Keywords that could be used to find the correct information in the OneNotebook are marked in bold throughout this document.

Short vignettes for each MTXQCvX2 modules and other selected processes are summarised in the folder `man/vignettes/`.

[^1]: Shared link: https://1drv.ms/u/s!Aq56mkSqDxZjgTu-LvPV2xFTWWGu


### First steps:
   
    1. Download the current version of MTXQCvX2 from github.com/ChrisZasa/fluffy-adventure
    2. Create a new folder - directory of your Rproject.
    3. Initiate a new Rproject (.Rproj)
    4. Copy all files extracted from the zip-archive downloaded from github into this folder.
    5. Open MTXQC_init.Rmd (you are reading the knitted version of this file)
    6. Click the small triangle next to the Knit button and select: Knit with parameter
    7. Define a project folder name, e.g, HEK293_glucose
    8. Copy your Maui- or Metmax-derived input files into the corresponding folders
    9. Follow the detailed instructions (folder man/vignettes/*)

Once the folder structure in your project has been initiated and all required packages have been installed, 
proceed with copying all input files.

Detailed instructions for MAUI-projects and Metmax-extracted projects are described in the corresponding
vignettes - have a look at `man/vignettes/`.


```{r create_directory, message=FALSE, warning=FALSE,echo=FALSE}

source("R/MTXQC_init.R")
initiate_MTXQC(subfolder = params$spath)

```




