---
title: "Guide MTXQC project in R-studio"
author: "Christin"
date: "27 October 2017"
output: html_document
params:
  spath:
    input: text
    label: "Create MTXQCproject subfolder:"
    value: ""
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# How to use this guide

Welcome to the MTXQC universe.

This document provides you a quick guidance through the first steps of the MTXQC universe and how to setup your R-studio project. 

Detailed information to distinct steps are provided in addition in the MTXQC-OneNotebook [^1]. You need to setup a microsoft office account or need to remember your credentials. Keywords that could be used to find the correct information in the OneNotebook are marked in bold throughout this document.

Read this document step by step and follow the instructions. In case of confusion just ask one of your colleagues for hands-on help or send me an e-mail.

If you read the html-version of this document linked in the OneNotebook or extracted from the the MTXQCvX archive you are going to be asked to open the corresponding README.RMD file in R-Studio after you have setup your R project and to process it once. But step by step - further information are following. 

[^1]: Shared link: https://1drv.ms/u/s!Aq56mkSqDxZjgTu-LvPV2xFTWWGu

# Getting started
## Setup a R-project

Open R-studio and go to File -> New Project -> New directory.
Define a new project folder, e.g., 2017_CancerProfiles.

Open this folder in your windows explorer or in mac finder. You should find a little blue icon representing your R-project inside this folder.

## Copy files and folders

If you haven't openend the explorer or finder navigate to your R-project folder now and
copy the following folder from the MTXQC_template archive:
  
  1. R
  2. config_files
  
Copy also all Rmd-files you find in the MTXQC archive, e.g., MTXQC part 1-4 and README.RMD (that you are currently reading).


## Knit this document

Knit this document, recommendation htmp, in order to create all other required folder and subfolder in your R-project directory.

To do so click on the small ball of yarn few icons left from the icon disk that saves your files.

If you read the html version of this readme.rmd document please open R-studio, ipen your R-project and the README.RMD file. Knit the file and open the created hmtl output in a browser and keep reading at that place (much more comfy).

```{r create_directory, message=FALSE}

source("R/MTXQC_init.R")
initiate_MTXQC(subfolder = params$spath)

```




