---
title: 'MTXQCvX2 - Experimental Setup - PROJECT TITLE'
author:
- affiliation: LAB, LAB LOCATION 
  name: NAME ONE 
- affiliation: LAB, LAB LOCATION
  name: NAME TWO
params:
  subf:
    input: text
    label: "Run MTXQC based on data in subfolder:"
    value: "test"
  inputformat:
    input: select
    label: "Select the input format of your data"
    choices: [maui, metmax]
    value: maui
  ann:
    input: text
    label: "File name of your project annoation (.csv)"
    value: annotation.csv
  sample_ext:
    input: text
    label: "File name of your project sample extracts (.csv)"
    value: Sample_extracts.csv
  data:
    input: select
    choices: [qMTX, pSIRM, pSIRM time series]
    label: 'Type of performed experiment:'
    value: qMTX
  substr: 
    input: select
    multiple: FALSE
    choices: [glc, gln, pyr, other, multiple, none]
    label: 'Specify applied stable isotopes:'
    value: no
  instd:
    input: checkbox
    label: "Internal extraction standard applied:"
    value: TRUE
  samples:
    input: select
    multiple: FALSE
    choices: [cell extracts, blood/serum, tissue, supernatant, mixed]
    label: 'Specify the origin of samples:'
    value: mixed
  addQ:
    input: select
    label: "Include additional calibration curves for the absolute quantification."
    choices: ["yes", "no"]
    value: no
  addQ_Int:
    input: select
    label: "Integrate additional calibration curves into all batches of the project"
    choices: ["yes", "no"]
    value: yes
  quant:
    input: select
    choices: [Quant1_v3, Quant1_v4, Quant1_ind]
    label: "Quantification standards: "
    value: Quant1_v3
  quant_vol:
    input: text
    label: "Quant: Volume (ul) of dried polar phase after extraction"
    value: 500
  backups:
    input: text
    label: "Technical replicates per sample:"
    value: 1
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    keep_tex: yes
    latex_engine: pdflatex
    template: config_files/textemplate.tex
    toc: yes
fontfamily: mathpazo
date: '`r format(Sys.Date(), "%B %d, %Y")`'
fontsize: 10pt
geometry: margin = 1in
keywords: MTXQCvX, GC-MS, metabolomics, data analysis and processing
biblio-style: apsr
thanks: Kempa Lab - MTXQCvX ExperimentalSetup, provided by Ch. Zasada, processed '`r format(Sys.Date(), "%B %d, %Y")`'
abstract: This document provides an evaluation of GC-MS derived metabolomics data.
  It asseses GC-MS performance, the absolute quantification and the
  stable isotope incorporation. ADD HERE FURTHER PROJECT RELEVANT FACTS.
---

```{r setup_output, echo=FALSE}
#set path for figure export and size
#MOD!

set_input <-  "input/"
set_output <-  "output/"

#directory definition and figure_name definition
if (params$subf == "") {
  path_setup = ""
} else {
  path_setup <-  paste0(params$subf, "/")
}

knitr::opts_chunk$set(echo = FALSE,  #TRUE - show R code
                      warning = FALSE, #show warnings
                      message = TRUE,
                      eval = TRUE) #show messages
```
 

# Project-related experimental setup
<!-- 
Add here the the extraction protocol of your samples. Use this provided space 
to have a complete report starting from sample extraction, derivatisation and 
quantification or isotope incorporation 
                                                                          -->
                                                                          
                                                                          
Sample extraction and derivatisation have been performed by Jenny. 
According to her notes documented in OneNote section:
Collaborations/Landthaler/ODC1 experiment

# Sample extraction

Extraction protocol:
      
      1. 5 ml MeOH (50%)
      2. 1 ml Chlorform
      3. dried 3.5 ml of polar phase
      4. 2nd extraction: yes (in two replicates)

Polar phases have been split into two equal fractions of *280* ul (added 600 ul 20% MeOH).

# Quant-Mix extraction protocol

Quant-Mixes batch: *Quant_v4*

       1. 1 ml MCW for extraction
       2. 0.5 ml H2O for phase separation
       3. dried 0.5 ml of polar phase (twice)
  

# Derivatisation protocol

Applied the following protocol for derivatisation protocol

      1. MEOX/Pyridine (final conc: 40 mg MEOX/ 1 ml Pyridine)
        - Volume: 20 ul
        - Incubation time: 90 min
        - Temp: 30 C
      2. Alkan-mix/MSTFA (10 ul mix/1 ml MSTFA)
        - Volume: 80 ul
        - Incubation time: 60 min
        - Temp: 37 C
        
Prepared aliquots: three-times 28 ul, big glas vials, crimped.

# GC-MS measurement

Samples have been measured using the following methods

      1. Injector-method: hamilton_1ul
      2. GC-method: 5/7/12 1.2ml/min
      3. Split: 1:5
      4. MS-method: Lizzy-like
      


# General MTXQC parameter
```{r par_table}

source("R/MTXQC_fcn.R")
source("R/MTXQC_config.R")

par_table <-  export_MTXQCsetup(params, path_setup, file_spec, "ExpSetup")

table_print <-  as.data.frame(par_table)
knitr::kable(table_print, format = "pandoc", caption = "Experimental parameters of the project.")

```
